---
title: "Global Land-Ocean Temperature Index Data Exploration"
output: html_notebook
---

```{r setup}
library(tidyverse)

```
## Load Data

Data has been downloaded from the link below. CSV file has been saved locally in data sub-folder.

<https://data.giss.nasa.gov/gistemp/tabledata_v4/GLB.Ts+dSST.csv>

```{r firstLoad}
df <- read_csv("../data/GLB.Ts+dSST.csv")

head(df)

```

First row of csv file contains header text that is not required, reload data skipping the first row.

```{r loadDataAndSkip}
df <- read_csv("../data/GLB.Ts+dSST.csv",
               skip = 1)

head(df)
```

NA values appear as three asterisks, so reload data and convert *** to NA values

```{r loadDataAndSkipAndNA}
df <- read_csv("../data/GLB.Ts+dSST.csv",
               skip = 1,
               na = "***")

head(df)
```

19 variables are shown, looking at the data types, all appear to be numeric. 

```{r}
str(df)
```

Two variables that contain - characters, use the clean_names() function from the janitor package to tidy the variable names. 

```{r}
df <- read_csv("../data/GLB.Ts+dSST.csv",
               skip = 1,
               na = "***")

df <- df %>% janitor::clean_names()

head(df)

str(df, give.attr = FALSE)

```

